Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-14 paper/paper.tex

\emph{Related Ideas.}\Mar{Summarize Test Transplantation.} It is worth
noting that Differential Testing~\cite{Brumley-etal-ss07} (DT) has
been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated---as only one engine is used, the outcomes
of the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of these techniques aforementioned in finding
bugs on \javascript\ engines.

@@

\section{Related Work}

>>>>

The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
assumption behind test set diversity is that faults often spread
contiguously in the input domain. Consequently, it should be
beneficial to partition the input domain and explore it more evenly as
to find bugs faster. Later in the nineties, Chen and
Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
the continuity assumption. They found that faults, most open, manifest
themselves in regular patterns across the input
domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
observations led researchers to investigate generalizations of the
approach to non-numerical data types and strategies to explore the
input (or output) space to solve different problems in Software
Engineering (\eg{}, test input generation and test
selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
paper explores diversity of sources of test cases and diversity of
engines to test and find bugs. We remain to investigate the diversity
of test cases themselves. In principle, that could help reduce the
number of alarms to inspect, for example.

\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In constrast
to prior work on test set diversity, this paper explores diversity of
sources of test cases and diversity of implementations with the goal
of finding bugs. Section~\ref{sec:related-work} elaborates related
work on this topic. Differential Testing~\cite{Brumley-etal-ss07} (DT)
has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated---as only one engine is used, the outcomes
of the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of these techniques aforementioned in finding
bugs on \javascript\ engines.

@@

\section{Related Work}
\label{sec:related-work}
